Accuracy and precision of zero-heat-flux temperature monitoring

### 2019-12-05 manuscript/manuscript.Rmd
author updated html

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring"
subtitle: A systematic review and meta-analysis
description: "A systematic review and meta-analysis"
author:
- name: Aaron Conway
  affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: aaron.conway@utoronto.ca
  url: https://www.aaronconway.info
- name: Megan Bittner
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Dan Phan
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Navpreet Kamboj
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: navpreet.kamboj@mail.utoronto.ca
- name: Kristina Chang
  affiliation: Toronto General Hospital, UHN
- name: Peter Collins
  affiliation: Toronto General Hospital, UHN
- name: Elizabeth Tipton
  affiliation: Department of Statistics, Northwestern University
- name: Matteo Parotto
  affiliation: Toronto General Hospital, UHN
date: "`r Sys.Date()`"
repository_url: https://github.com/awconway/zhf-review
twitter:
  creator: "@aw_conway"
bibliography: Extras/bibliography.bib
csl: Extras/anesthesiology.csl
# author:
#   - Aaron Conway PhD:
#       email: aaron.conway@utoronto.ca
#       institute: [PMCC, LBFON, QUT]
#       correspondence: true
#   - Megan Bittner BSc:
#       institute: [LBFON]
#       correspondence: false
#   - Dan Phan BSc:
#       institute: [LBFON]
#       correspondence: false
#   - Kristina Chang MScN:
#       institute: [TGH]
#       correspondence: false
#   - Elizabeth Tipton PhD:
#       institute: [NW]
#       correspondence: false
#   - Matteo Parotto MD:
#       institute: [TGH]
#       correspondence: false
# institute:
#   - PMCC: Peter Munk Cardiac Centre, University Health Network
#   - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   - QUT: School of Nursing, Queensland University of Technology (QUT)
#   - TGH: Toronto General Hospital, UHN
#   - NW: Department of Statistics, Northwestern University
# output:
#   bookdown::word_document2:
#     reference_docx: Extras/manuscript_template.docx
#     pandoc_args:
#       - --csl=Extras/anesthesiology.csl
#       - --lua-filter=Extras/scholarly-metadata.lua
#       - --lua-filter=Extras/author-info-blocks.lua
output: distill::distill_article
params:
  distill: TRUE
  word: FALSE
---

>>>>

---
title: "Accuracy and precision of zero-heat-flux temperature monitoring"
subtitle: A systematic review and meta-analysis
description: "A systematic review and meta-analysis"
author:
- name: Aaron Conway
  affiliation: Peter Munk Cardiac Centre, UHN & Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: aaron.conway@utoronto.ca
  url: https://www.aaronconway.info
- name: Megan Bittner
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Dan Phan
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
- name: Navpreet Kamboj
  affiliation: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
  email: navpreet.kamboj@mail.utoronto.ca
- name: Kristina Chang
  affiliation: Toronto General Hospital, UHN
- name: Elizabeth Tipton
  affiliation: Department of Statistics, Northwestern University
- name: Matteo Parotto
  affiliation: Toronto General Hospital, UHN
date: "`r Sys.Date()`"
repository_url: https://github.com/awconway/zhf-review
twitter:
  creator: "@aw_conway"
bibliography: Extras/bibliography.bib
csl: Extras/anesthesiology.csl
# author:
#   - Aaron Conway PhD:
#       email: aaron.conway@utoronto.ca
#       institute: [PMCC, LBFON, QUT]
#       correspondence: true
#   - Megan Bittner BSc:
#       institute: [LBFON]
#       correspondence: false
#   - Dan Phan BSc:
#       institute: [LBFON]
#       correspondence: false
#   - Kristina Chang MScN:
#       institute: [TGH]
#       correspondence: false
#   - Elizabeth Tipton PhD:
#       institute: [NW]
#       correspondence: false
#   - Matteo Parotto MD:
#       institute: [TGH]
#       correspondence: false
# institute:
#   - PMCC: Peter Munk Cardiac Centre, University Health Network
#   - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto
#   - QUT: School of Nursing, Queensland University of Technology (QUT)
#   - TGH: Toronto General Hospital, UHN
#   - NW: Department of Statistics, Northwestern University
# output:
#   bookdown::word_document2:
#     reference_docx: Extras/manuscript_template.docx
#     pandoc_args:
#       - --csl=Extras/anesthesiology.csl
#       - --lua-filter=Extras/scholarly-metadata.lua
#       - --lua-filter=Extras/author-info-blocks.lua
output: distill::distill_article
params:
  distill: TRUE
  word: FALSE
---
